%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{qrcode}
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Steven Dirth}}}}}
	
	\vspace{6pt}
	
	{\huge Software Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.03\textwidth} % 2% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	{\large
		\faPhone \\
		\faEnvelope \\
		\faLink \\
		\faGithub \\
		\faLinkedin
	}
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 58% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	{\large
		\href{tel:15636072806}{+1 563 607 2806} \\
		\href{mailto:resume19f@stevendirth.com}{resume19f@stevendirth.com} \\
		\href{https://stevendirth.com}{stevendirth.com} \\
		\href{https://github.com/dirthsj}{github.com/dirthsj} \\
		\href{https://linkedin.com/in/stevendirth}{linkedin.com/in/stevendirth}
	}
\end{minipage}
\begin{minipage}[t]{0.20\textwidth} % 20% of the page for the qr code
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\hfill \qrcode{https://stevendirth.com}

\end{minipage}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------


\vspace{0.5cm}

\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}

		\baritem{Git}{80}
		\baritem{C/C++}{90}
		\baritem{C\#/.NET}{70}

	\end{barchart}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}

		\baritem{Azure}{60}
		\baritem{Java}{70}
		\baritem{Angular}{60}

	\end{barchart}
\end{minipage}


%\begin{center}
%	\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
%\end{center}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2017 -- 2021}
		{Bachelor's Degree}
		{Iowa State University}
		{Dean's List Fall 2017 | Spring 2018}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Work Experience}

\begin{entrylist}
	\entry
		{May -- Aug 2019}
		{Software Developer Intern -- Data Science \& Informatics}
		{Corteva Agriscience}
		{I redesigned a solution for moving and managing data between systems using .NET, .NET Core, Entity Framework Core, Azure, and Angular. The backend for the project was done using Azure Functions serving as both the web API and data processor. The frontend was written in Angular 5 utilizing Typescript and SCSS. I also created a windows service to load data into the backend. I used Azure DevOps, Artifactory, and Octopus Deploy for deployment.}
	\entry
		{May -- Aug 2018}
		{Test Department Intern}
		{Sears Seating}
		{I performed various tests (both automated and manual) on a number of seats.  This included designing the test, setup, data recording, and teardown.  The major project I worked on was a semi-automated test involving an environment chamber, a NI cRIO, several sensors and multiple actuators}
	\entry
		{2018 and prior}
		{Various Employment}
		{Iowa State University, Monsanto Company}
		{I worked for ISU Dining during the 2nd semester of the 2017-2018 school year.  I also worked for Monsanto the two summers before that.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\cvsect {Projects}
\begin{entrylist}
	\entry
		{2017 --}
		{Asteroid}
		{Cardinal Space Mining}
		{A cross platform desktop application written in C++ using the Qt and boost frameworks.  The application acts as a control panel for CSM's robots}
	\entry
		{2017 -- 2018}
		{Pavonis}
		{Cardinal Space Mining}
		{The main robot control software which runs on a Xilinx MicroZed.  The software is written in C++ using the boost libraries and is cross compiled for the MicroZed.  Many improvements were made this year, but the most important was the distributed sensing protocol which allows the addition or removal of sensors without requiring any code changes to this project.}
	\entry
		{2018 -- 2019}
		{Marineris}
		{Cardinal Space Mining}
		{The main robot control software which runs on a Xilinx MicroZed.  The software is written in C++ using the boost libraries and is cross compiled for the MicroZed.  A major improvement this year was to the motor communication, as we were able to get sensor feedback from the motor controllers.}\
	\entry
		{2017}
		{Development Server}
		{Cardinal Space Mining}
		{I set up and maintain an Ubuntu server which hosts a GitLab runner for continuous integration and unit tests, as well as provides a way for new members to compile code without installing a virtual machine or full blown linux on their personal devices.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ACTIVITIES AND HONORS
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.17\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Activities}
	
	2019 -- \\
	2017 -- \\
	2016 -- 17 \\
	2016 -- 17 \\
	2016 -- 17 \\
	2014 -- 17 \\

\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\vspace{13mm}

	\textbf{Controls Project Director}\hfill Cardinal Space Mining \\
	\textbf{Developer}\hfill Cardinal Space Mining \\
	\textbf{Member}\hfill National Honor Society \\
	\textbf{Developer}\hfill FIRST Robotics Competition \\
	\textbf{Co-Captain}\hfill FIRST Tech Challenge \\
	\textbf{Developer}\hfill FIRST Tech Challenge \\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Honors}

	ISU Dean's List \hfill Spring 2018 \\
	ISU Dean's List \hfill Fall 2017 \\
	Eagle Scout \hfill July 2016 \\

\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
